A thermodynamic view of dusty protoplanetary disks I: axisymmetric stability

### 2017-04-24 model.tex
edits from discussion with andrew

Notice Eq. \ref{eos} resembles an ideal gas equation of state but with  
effective temperature $T_\mathrm{eff} = 
T_\mathrm{ref}\left(1-\tepsilon\right)$. %sound-speed $c_{s,\mathrm{eff}} = c_s\sqrt{\left(1 -
This effective mixture  
temperature is lowered with dust-loading. 
%   \tepsilon\right)}$. 
%then the equation of state has the standard
%form $P=c_{s,\mathrm{eff}}^2\rho$. 
Since $\tepsilon$ typically decrease away from the midplane, we expect
vertically isothermal dusty disks to in fact behave as if it had a
temperture \emph{increasing} away from $z=0$.

@@

In this work, we assume that $\tstop$  is sufficiently small so
that settling occurs on much longer timescales  than that of interest; or
consider equilibria with $\mathcal{C}\equiv 0$, namely   
\begin{inparaenum}[1)] 
\item 
  unstratified disks with finite dust-gas drag; %(\S\ref{si});  
\item 
  perfectly-coupled dust with $\tstop=0$. %(\S\ref{results}). 
\end{inparaenum} 
Vertical settling is absent in both cases.

@@

In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
%&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
  \sigma^2\mathcal{I}^2
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV,\label{int_rel}
\end{align} 
%The real integral $\mathcal{I}^2>0$ 
where
\begin{align}
  \mathcal{I}^2 \equiv \int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV
\end{align}
is the meridional kinetic energy, 
and coefficients $A,B,C,D$ can be
read off Eq. \ref{integral_ex}. %Note that $B=C$ from dynamical equilibrium
%(Eq. \ref{vshear}). 
We now consider various limits of Eq. \ref{int_rel}.

@@

In this case, the last two integrals in Eq. \ref{int_rel} vanish. Then 
requiring $\sigma^2>0$  gives the criteria 
for the axisymmtric \emph{stability} of an isothermal gas perfectly 
coupled to dust,  
\begin{align}
  \kappa^2 + c_s^2 \nabla\ln{\rhog}\cdot\nabla\tepsilon &> 0,\label{dusty_solberg1}  \\
  -c_s^2\frac{\p\ln{\rhog}}{\p z}\left(-\kappa^2\frac{\p\tepsilon}{\p
    z} + r\frac{\p\Omega^2}{\p z}\frac{\p \tepsilon}{\p r} \right) & > 0, \label{dusty_solberg2}
\end{align} 
%\begin{align}
%  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0, \label{dusty_solberg1}    \\
%  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
%  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, \label{dusty_solberg2}
%\end{align} 
where %$s = \ln{P/\rho}$, 
$\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)>0$ is the 
square of the epicylic frequency. %We assume $\kappa^2>0$.  
Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2} are in fact the 
the Solberg-Hoiland criteria for axisymmetric stability of adiabatic
gas if one inserts $C_p\ln{\left(1 -
    \tepsilon\right)}$ for the entropy in the standard
expression for said criteria \citep{tassoul78}.

\subsubsection{Order-of-magnitude estimates} 
We evaluate the above stability criteria for the vertically-Gaussian
distributions for the gas density and the dust-to-gas ratio as 
described in \S\ref{eqm}. 
%However, here we permit 
%$\epsilon_0=\epsilon_0(r)$ and $\Htilde=\Htilde(r)$ to vary with
%radius. 
We assume the disk is approximately Keplerian so that
$\kappa\simeq\OmK$. In terms of the dust-to-gas
ratio $\epsilon$, Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2}
become   
\begin{align}
  &1 + \frac{\epsilon}{\left(1+
    \epsilon\right)^2}\left(h_\mathrm{g}^2\frac{\p\ln{\rhog}}{\p\ln{r}}
  \frac{\p\ln{\epsilon}}{\p\ln{r}} + 
  \frac{z^2}{\Htilde^2}\right)>0 \label{stability_est1},   \\ 
&1 - \frac{\epsilon
  h_\mathrm{g}^2}{\left(1+\epsilon\right)^2}
  \frac{\p\ln{\epsilon}}{\p\ln{r}}\left(-\frac{\p\ln{\rhog}}{\p\ln{r}}+\frac{\Htilde^2}{H_\mathrm{g}^2}\frac{\p\ln{\epsilon}}{\p\ln{r}}\right)
  > 0 \label{stability_est2},
\end{align}
\emph{for stability}.

>>>>

Notice Eq. \ref{eos} resembles an ideal gas equation of state but with  
a reduced temperature $\tilde{T} = 
T_\mathrm{ref}\left(1-\tepsilon\right)$. %sound-speed $c_{s,\mathrm{eff}} = c_s\sqrt{\left(1 -
This effective mixture  
temperature is lowered with dust-loading. 
%   \tepsilon\right)}$. 
%then the equation of state has the standard
%form $P=c_{s,\mathrm{eff}}^2\rho$. 
Since $\tepsilon$ typically decrease away from the midplane, we expect
vertically isothermal dusty disks to in fact behave as if it had a
temperture \emph{increasing} away from $z=0$.

@@

In this work, consider equilibria with $\mathcal{C}\equiv 0$, namely   
\begin{inparaenum}[1)] 
\item 
  unstratified disks with finite dust-gas drag; %(\S\ref{si});  
\item 
  perfectly-coupled dust with $\tstop=0$. %(\S\ref{results}). 
\end{inparaenum} 
Vertical settling is absent in both cases. Alternatively, we are 
assuming that $\tstop$  is sufficiently small such 
that settling occurs on much longer timescales than the instabilities of interest.

@@

In Appendix
\ref{var_prin} we derive the integral relation,  
\begin{align}
%&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
  \sigma^2\mathcal{I}^2
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \left(\dd v_z \dd v_r^* + \dd v_z^*\dd v_r\right) B +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\Bigl\lvert \nabla\cdot\left(P\dd
  \bm{v}\right)\Bigr\rvert^2\right]dV  -\int \left(\nabla\cdot\dd\bm{v}^*\right)\dd\mathcal{C}dV \notag\\
&\phantom{===}
- \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV,\label{int_rel}
\end{align} 
%The real integral $\mathcal{I}^2>0$ 
where
\begin{align}
  \mathcal{I}^2 \equiv \int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV
\end{align}
is the meridional kinetic energy, 
and coefficients $A,B,D$ be
read off Eq. \ref{integral_ex}. %Note that $B=C$ from dynamical equilibrium
%(Eq. \ref{vshear}). 
We now consider various limits of Eq. \ref{int_rel}.

@@

In this case, the last two integrals in Eq. \ref{int_rel} vanish. 
The condition for axisymmtric \emph{stability}, $\sigma^2>0$, 
is met if the integrand cofficients satisfy $A+D>0$ and $AD-B^2>0$
\citep[][Section 11.6]{ogilvie16}, which becomes 
\begin{align}
  \kappa^2 + c_s^2 \nabla\ln{\rhog}\cdot\nabla\tepsilon &> 0,\label{dusty_solberg1}  \\
  -c_s^2\frac{\p\ln{\rhog}}{\p z}\left(-\kappa^2\frac{\p\tepsilon}{\p
    z} + r\frac{\p\Omega^2}{\p z}\frac{\p \tepsilon}{\p r} \right) & > 0, \label{dusty_solberg2}
\end{align} 
%\begin{align}
%  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0, \label{dusty_solberg1}    \\
%  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
%  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, \label{dusty_solberg2}
%\end{align} 
where %$s = \ln{P/\rho}$, 
$\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)>0$ is the 
square of the epicylic frequency. %We assume $\kappa^2>0$.  
Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2} are in fact the 
the Solberg-Hoiland criteria for axisymmetric stability of adiabatic
gas if one inserts $C_p\ln{\left(1 -
    \tepsilon\right)}$ for the entropy in the standard
expression for said criteria \citep{tassoul78}.

\subsubsection{Order-of-magnitude estimates} 
We evaluate the above stability criteria for the equilibria described in \S\ref{eqm}. 
%However, here we permit 
%$\epsilon_0=\epsilon_0(r)$ and $\Htilde=\Htilde(r)$ to vary with
%radius. 
We assume the disk is approximately Keplerian so that $\kappa\simeq\OmK$, and that the vertical gas distribution is
Gaussian. In terms of the dust-to-gas
ratio $\epsilon$, Eq. \ref{dusty_solberg1}---\ref{dusty_solberg2}
become   
\begin{align}
  &1 + \frac{\epsilon}{\left(1+
    \epsilon\right)^2}\left(h_\mathrm{g}^2\frac{\p\ln{\rhog}}{\p\ln{r}}
  \frac{\p\ln{\epsilon}}{\p\ln{r}} + 
  \frac{z^2}{\Htilde^2}\right)>0 \label{stability_est1},   \\ 
&1 - \frac{\epsilon
  h_\mathrm{g}^2}{\left(1+\epsilon\right)^2}
  \frac{\p\ln{\epsilon}}{\p\ln{r}}\left(-\frac{\p\ln{\rhog}}{\p\ln{r}}+\frac{\Htilde^2}{H_\mathrm{g}^2}\frac{\p\ln{\epsilon}}{\p\ln{r}}\right)
  > 0 \label{stability_est2},
\end{align}
\emph{for stability}.

### 2017-04-24 summary.tex
typo in generalized PV
edits from discussion with andrew

\subsubsection{Classic gravitational instabilities} %vertical structure 
The addition of dust enhances gravitational
instability (GI). This is because dust particles contribute to the
total disk mass but not thermal pressure, which effectively lowers the
disk temperature \citep[][]{thompson88,shi13}. For typical dust-loading 
$\epsilon, Z\ll1$, this effect is unimportant. However, if $\epsilon$ is
large (e.g. due to dust settling) then the effective temperature may 
be lowered to enable instability.

As noted in \S\ref{loc_iso_eos}, dust settling causes the effective
temperature to \emph{increase} away from the midplane. This contrasts
to previous studies of GI in vertically stratified disks
 where the temperature decreases
from the midplane \citep[e.g.][]{mamat10, kim12,lin14c}. 
While we expect only the total surface density and
characteristic temperatures are relevant to stability  
\citep{toomre64}, a non-trivial effective vertical temperature
structure, induced by dust, may modify the vertical structure of 3D
waves and unstable modes. We will examine this linear problem in a following 
study.

@@

\subsubsection{Rossby wave instability}
The Rossby wave instability (RWI) is a non-axisymmetric, 2D shear
instability that operates in thin disks when it has radial structure
\citep{lovelace99,li00}. These studies consider adiabatic pure gas and 
show instability is possible if there is an extrema in the generalized
potential vorticity 
\begin{align}
 \mathcal{V} = \frac{\kappa^2}{2\Omega\Sigma}\mathcal{S}^{2/\gamma},  
\end{align} 
where $\mathcal{S} = \Pi/\Sigma^\gamma$. Here, $\Sigma$ is the total
surface density and $\Pi$ is the vertically integrated pressure.

@@

\subsection{New dust-drag
  instabilities}\label{dust_as_thermo}

%{\bf vsi enabled by drag? slipping between dust and gas reduces
 % effective buoyancy}

As described in \S\ref{dust_work}, 
the physical cause of dust-drag instabilities is a phase lag between
the pressure and density response in a dusty gas\footnote{
In fact, we expect a phase difference between pressure and the total
density  whenever $\tstop\neq0$; not just $\tstop\OmK\ll 1$ as 
considered in this work. This is simply because of the finite
relaxation time required for dust to respond to gas, and vice versa. 
An effective energy equation in the form of Eq. \ref{eff_energy} can
still be obtained for general $\tstop$. The
heat flux $\bm{F}$ in the cooling function $\mathcal{C}$ is determined
through solution to the relative velocity $\Delta \bm{v} =
\bm{v}_\mathrm{d}-\bm{v}_\mathrm{g}$ \citep{youdin05a,laibe14}.  We
thus expect the `pressure-density lag' interpretation of dust-drag 
instabilities to be generally applicable.}. 
This may be used to re-interpret the streaming instability or to
understand other dusty instabilities. For example,
\cite{loren15,loren16} have recently discovered a new axisymmetric 
instability in their two-fluid numerical simulations of dusty
protoplanetary disks. They find it leads to the formation of
`toroidal vortices'.

%give numerical example 
We have applied our one-fluid stability analysis to find unstable modes  
similar to that described by \cite{loren15}. We use the same
parameters reported by them as follows. 
%we set $p=q=0$, which eliminates VSI and minimizes streaming
%instabilities as there is no radial pressure gradient at the disk
%midplane.   
The total metalicity is $Z=0.01$ and the dust scale-height $H_\mathrm{d} =
0.4H_\mathrm{g}$, giving a maximum dust-to-gas ratio
$\mathrm{max}(\epsilon) = 0.025$. The midplane stopping time is 
$t_\mathrm{s0}=0.02\OmK^{-1}$. The gas disk parameters are $(p,q,
\hgas) =(-1.5, -1,0.05)$.  We set $k_x = \pi/H_\mathrm{d}$.

Fig. \ref{compare_eigenvals_ts0d02} shows the unstable modes found for
this setup. We find the usual VSI modes, here with $\omega> 3\hgas\OmK,\, s<
0.2\hgas\OmK$. However, we also find modes with $\omega<s$. One of these,
marked by the blue asterisk, has 
frequency 
\begin{align*}
\sigma = (0.3631\ii - 0.1251)\hgas\OmK. 
\end{align*}
This growth rate corresponds to $8.8$ orbits, comparable to the $12$
orbits reported by \citeauthor{loren15}. We visualize this mode in
Fig. \ref{result2d_loren}. We find this mode 
persists when $q=0$, so it is not the VSI. 
Using Eq. \ref{streaming_dispersion} with the above parameters,  
we also estimate a much smaller growth 
rate for the streaming instability of 
$O(10^{-3}\hgas\OmK)$, We thus also rule out
SI, as did \citeauthor{loren15}. However, the mode disappears with $\tstop=0$, so it \emph{is}
associated with finite dust-gas drag.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_eigenvals_ts0d02}
  \caption{Unstable modes in a locally isothermal, dusty disk
    with stopping time  
    $\tstop=0.02\OmK^{-1}$. Modes with $\omega>3$ are due to
    VSI. The mode marked by the blue asterisk, visualized in
    Fig. \protect\ref{result2d_loren}
    , is associated with finite dust-gas
    drag. 
  }\label{compare_eigenvals_ts0d02}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/result2d_loren.ps}
  \caption{Visualization of the mode marked by the blue asterisk in
    Fig. \protect\ref{compare_eigenvals_ts0d02}. 
    This is a possible eigenmode of the dusty instability discovered by  
    \cite{loren15} in their numerical simulations. The instability growth timescale and 
    radial spacing of the `toroidal vortices' are similar to that 
    reported by \citeauthor{loren15}. This instability is driven by
    dust-gas drag. The color scale shows the 
    perturbed  
    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
  }\label{result2d_loren}
\end{figure}

One possible interpretation of this mode is `drag-driven VSI', to be 
compared with `cooling-driven VSI' studied by \cite{lin15}. In the
latter case, buoyancy forces are eliminated by fast
cooling, allowing vertical shear to destabilize the disk. Now, in an
isothermal dusty disk if $\tstop=0$ then mixture is 
effectively adiabatic: dust-induced buoyancy forces are
strongest. However, having $\tstop\neq0$ allow dust particles to slip
past the gas, reducing buoyancy. That is, dust-gas drag
provies an effective cooling.

We stress that this example only serves to highlight
the possibility of new axisymmetric dust-drag instabilities in
stratified disks. A major caveat of the above result is that 
%the base state is not an exact equilibrium, because dust-settling would occur
%in practice. (
 the background dust settling timescale is comparable to the instability
growth timescale. It is essential to construct
exact equilibria for a meaningful stability analysis. We defer this
to future work.

%also unclear what are "proper" vertical bc for dusty disks

>>>>

\subsubsection{Classic gravitational instabilities} %vertical structure 
The addition of dust enhances gravitational
instability (GI). This is because dust particles contribute to the
total disk mass but not thermal pressure, which effectively lowers the
disk temperature \citep[][]{thompson88,shi13}. For typical dust-loading 
$\epsilon, Z\ll1$, this effect is unimportant. However, if $\epsilon$ is
large (e.g. due to dust settling) then the reduced temperature $\tilde{T}$ may 
be lowered to enable instability.

As noted in \S\ref{loc_iso_eos}, dust settling causes 
$\tilde{T}$ to \emph{increase} away from the midplane. This contrasts
to previous studies of GI in vertically stratified disks
 where the temperature decreases
from the midplane \citep[e.g.][]{mamat10, kim12,lin14c}. 
While we expect only the total surface density and
characteristic temperatures are relevant to stability  
\citep{toomre64}, a non-trivial effective vertical temperature
structure, induced by dust, may modify the vertical structure of 3D
waves and unstable modes. We will examine this linear problem in a following 
study.

@@

\subsubsection{Rossby wave instability}
The Rossby wave instability (RWI) is a non-axisymmetric, 2D shear
instability that operates in thin disks when it has radial structure
\citep{lovelace99,li00}. These studies consider adiabatic pure gas and 
show instability is possible if there is an extrema in the generalized
potential vorticity 
\begin{align}
 \mathcal{V} = \frac{\kappa^2}{2\Omega\Sigma}\mathcal{S}^{-2/\gamma},  
\end{align} 
where $\mathcal{S} = \Pi/\Sigma^\gamma$. Here, $\Sigma$ is the total
surface density and $\Pi$ is the vertically integrated pressure.

@@

% \subsection{New dust-drag
%   instabilities}\label{dust_as_thermo}

% %{\bf vsi enabled by drag? slipping between dust and gas reduces
%  % effective buoyancy}

% As described in \S\ref{dust_work}, 
% the physical cause of dust-drag instabilities is a phase lag between
% the pressure and density response in a dusty gas\footnote{
% In fact, we expect a phase difference between pressure and the total
% density  whenever $\tstop\neq0$; not just $\tstop\OmK\ll 1$ as 
% considered in this work. This is simply because of the finite
% relaxation time required for dust to respond to gas, and vice versa. 
% An effective energy equation in the form of Eq. \ref{eff_energy} can
% still be obtained for general $\tstop$. The
% heat flux $\bm{F}$ in the cooling function $\mathcal{C}$ is determined
% through solution to the relative velocity $\Delta \bm{v} =
% \bm{v}_\mathrm{d}-\bm{v}_\mathrm{g}$ \citep{youdin05a,laibe14}.  We
% thus expect the `pressure-density lag' interpretation of dust-drag 
% instabilities to be generally applicable.}. 
% This may be used to re-interpret the streaming instability or to
% understand other dusty instabilities. For example,
% \cite{loren15,loren16} have recently discovered a new axisymmetric 
% instability in their two-fluid numerical simulations of dusty
% protoplanetary disks. They find it leads to the formation of
% `toroidal vortices'.

% %give numerical example 
% We have applied our one-fluid stability analysis to find unstable modes  
% similar to that described by \cite{loren15}. We use the same
% parameters reported by them as follows. 
% %we set $p=q=0$, which eliminates VSI and minimizes streaming
% %instabilities as there is no radial pressure gradient at the disk
% %midplane.   
% The total metalicity is $Z=0.01$ and the dust scale-height $H_\mathrm{d} =
% 0.4H_\mathrm{g}$, giving a maximum dust-to-gas ratio
% $\mathrm{max}(\epsilon) = 0.025$. The midplane stopping time is 
% $t_\mathrm{s0}=0.02\OmK^{-1}$. The gas disk parameters are $(p,q,
% \hgas) =(-1.5, -1,0.05)$.  We set $k_x = \pi/H_\mathrm{d}$.

% Fig. \ref{compare_eigenvals_ts0d02} shows the unstable modes found for
% this setup. We find the usual VSI modes, here with $\omega> 3\hgas\OmK,\, s<
% 0.2\hgas\OmK$. However, we also find modes with $\omega<s$. One of these,
% marked by the blue asterisk, has 
% frequency 
% \begin{align*}
% \sigma = (0.3631\ii - 0.1251)\hgas\OmK. 
% \end{align*}
% This growth rate corresponds to $8.8$ orbits, comparable to the $12$
% orbits reported by \citeauthor{loren15}. We visualize this mode in
% Fig. \ref{result2d_loren}. We find this mode 
% persists when $q=0$, so it is not the VSI. 
% Using Eq. \ref{streaming_dispersion} with the above parameters,  
% we also estimate a much smaller growth 
% rate for the streaming instability of 
% $O(10^{-3}\hgas\OmK)$, We thus also rule out
% SI, as did \citeauthor{loren15}. However, the mode disappears with $\tstop=0$, so it \emph{is}
% associated with finite dust-gas drag.

% \begin{figure}
%   \includegraphics[width=\linewidth]{figures/compare_eigenvals_ts0d02}
%   \caption{Unstable modes in a locally isothermal, dusty disk
%     with stopping time  
%     $\tstop=0.02\OmK^{-1}$. Modes with $\omega>3$ are due to
%     VSI. The mode marked by the blue asterisk, visualized in
%     Fig. \protect\ref{result2d_loren}
%     , is associated with finite dust-gas
%     drag. 
%   }\label{compare_eigenvals_ts0d02}
% \end{figure}

% \begin{figure}
%   \includegraphics[width=\linewidth]{figures/result2d_loren.ps}
%   \caption{Visualization of the mode marked by the blue asterisk in
%     Fig. \protect\ref{compare_eigenvals_ts0d02}. 
%     This is a possible eigenmode of the dusty instability discovered by  
%     \cite{loren15} in their numerical simulations. The instability growth timescale and 
%     radial spacing of the `toroidal vortices' are similar to that 
%     reported by \citeauthor{loren15}. This instability is driven by
%     dust-gas drag. The color scale shows the 
%     perturbed  
%     dust-to-gas ratio, $\delta\epsilon$; and the arrows show
%     $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$. 
%   }\label{result2d_loren}
% \end{figure}

% One possible interpretation of this mode is `drag-driven VSI', to be 
% compared with `cooling-driven VSI' studied by \cite{lin15}. In the
% latter case, buoyancy forces are eliminated by fast
% cooling, allowing vertical shear to destabilize the disk. Now, in an
% isothermal dusty disk if $\tstop=0$ then mixture is 
% effectively adiabatic: dust-induced buoyancy forces are
% strongest. However, having $\tstop\neq0$ allow dust particles to slip
% past the gas, reducing buoyancy. That is, dust-gas drag
% provies an effective cooling.

% We stress that this example only serves to highlight
% the possibility of new axisymmetric dust-drag instabilities in
% stratified disks. A major caveat of the above result is that 
% %the base state is not an exact equilibrium, because dust-settling would occur
% %in practice. (
%  the background dust settling timescale is comparable to the instability
% growth timescale. It is essential to construct
% exact equilibria for a meaningful stability analysis. We defer this
% to future work.

% %also unclear what are "proper" vertical bc for dusty disks
